---
title: "Ocgrtools"
author: "Anna Posacka"
date: "December 6, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Ocgrtools** lets you to create speady plots of ocean property depth profiles and contains a dataset to go with it. This dataset is part of the study that was focused on investigating the **biogeochemical cycling of copper in the subarctic NE Pacific**, more information on the data and the study can be found [in this public repo](https://github.com/AnnaMagdalena/DCu_LineP-Subarctic-Pacific).

***
####The problem####
One of the most important visualizations of oceanographic data is the use of **depth profiles**. Depth profiles are plotted with depth along the vertical axis (y-axis) where seasurface represents 0m and is plotted at the top axis and deepest waters (eg. 2000m) are plotted at the bottom of y-axis. The range on the horizontal axis (x-axis) represents the range in the ocean property being plotted. Using any plot functions, be it R base or ggplot renders a graph where depths representing 0m occur at the bottom of the y-axis and the deepest depths occur at the top of the y-axis, which is counterinuitive to visualization of properties with depth. As such each time these ocean properties are plotted the "plotter" is required to reverse the y-axis. The pplot (property plot) function in this packages allows to create such plots more readily
***
####Installation###

```{r}
 devtools::install_github("AnnaMagdalena/Ocgrtools")
```

####Demo###

Get this:
```{r}
library(ggplot2)
ggplot(dat,aes(x=dCu_kg,y=depth))+geom_point(aes(colour=stn),size=3)

library(Ocgrtools)
pplot(dat,"dCu_kg","depth")
```

Versus this:

```{r}
library(ggplot2)
ggplot(dat,aes(x=dCu_kg,y=depth))+geom_point(aes(colour=stn),size=3)
```

Use the included data to learn about chemistry of the North Pacific Ocean. Read some more about this dataset in the [vignette](https://github.com/AnnaMagdalena/Ocgrtools/blob/master/vignettes/Ocgrtools.Rmd)

```{r}
library(Ocgrtools)
dat <- CuLineP201127
head(dat)
```
