---
title: "Ocgrtools : tools for oceanographic data visualization"
author: "Anna Posacka"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

One of the most important visualizations of oceanographic data is the use of **depth profiles**. Depth profiles are plotted with depth along the vertical axis (y-axis) where seasurface represents 0m and is plotted at the top axis and deepest waters (eg. 2000m) are plotted at the bottom of y-axis. The range on the horizontal axis (x-axis) represents the range in the ocean property being plotted. Using any plot functions, be it R base or ggplot renders a graph where depths representing 0m occur at the bottom of the y-axis and the deepest depths occur at the top of the y-axis, which is counterinuitive to visualization of properties with depth. As such each time these ocean properties are plotted the "plotter" is required to reverse the y-axis. The pplot (property plot) function in this packages allows to create such plots more readily and also contains some custom plot esthetics. It is completely based on the ggplot package.
This package contains also contains a companion data product: CuLineP201127 that is a compilation
of various oceanograpic measurements obtained during Line P cruise in the subarctic NE Pacific. 

### The dataset

Inspect the variables

```{r}
library(Ocgrtools)
dat <- CuLineP201127
head(dat)
```

This dataset contains the following observations

Variable name|  Description |Units
-------------|--------------|-------
depth | depths at which data was collected |ranges from 0-2000m|
stn |Station | factor with 4 levels :P4-P26|
lat| latitude | degrees North|
lon |longitude |degrees East|
press| pressure | dbar|
depth_n| nominal depth | meters|
dCu_L |dissolved copper | nmol L-1|
dCu_kg|dissolved copper| nmol kg-1|
dens |density| kg m-3|
dens_pot|potential denisty, aka sigma| unitless|
pot_temp|potential temperature| Celcius|
spicy |variable spice| unitless|
sal|salinity|PSU|
temp|tempetature| Celcius|
oxy| dissolved oxygen|nmol kg-1|


###Test data visualization###

```{r}
library(ggplot2)
ggplot(dat,aes(x=phosph,y=dCu_kg))+geom_point(aes(colour=stn),size=3)

```

### Use of the property plot function :pplot

This is what the propert versus depth data looks like without any re-organization.Visually,this plot gives an impression that a property values at the bottom of y-axis are what you would expect them to be in deepest waters - where these values are actually plotted at the top-right of the graph

```{r}
library(ggplot2)
ggplot(dat,aes(x=dCu_kg,y=depth))+geom_point(aes(colour=stn),size=3)

```

This is the "fixed" depth profile with the pplot. Note that variables (in columns) are imported in the function as strings, hence " " need to be used for the variables to plot

```{r}
library(Ocgrtools)
pplot(dat,"dCu_kg","depth")

```

And, one more example using salinity as a variable

```{r}
library(Ocgrtools)
pplot(dat,"sal","depth")
```
